In this section, we describe our empirical strategy to estimate the causal effect of cutting road maintenance spending on different outcome variables. One key feature of our quasi-experiment design is the exogeneity of timing of the election. The timing of the election is determined by the natural expiration of the road maintenance tax levy, which is typically 5 years, and is not impacted by factors such as the prevailing economic conditions or whether a road tax levy was passed or failed in earlier years.

\subsection{Regression Discontinuity in Panel Data setting}

Suppose that local government in area $i$ and year $t$ has to conduct a referendum to renew their road tax levy. The referendum is conducted to determine whether the road maintenance tax levy should be renewed or not. Let $v_{it}$ be the vote share against the renewal tax levy and  $v^*$ be the threshold determining the result of the referedum (levy fails to renew if $v_{it} > v^*$). Let $F_{it} = 1(v_{it} > v^*)$ be an indicator to represent if the renewal road tax levy fails, and $y_{it}$ be some outcome variable of interest. We can write,

$$
y_{it} = \alpha + \theta F_{it} + \epsilon_{it}
$$

where $\alpha$ is the intercept, $\theta$ is the parameter of interest representing the causal effect of renewing a road tax levy and $\epsilon_{it}$ is the error term representing all other determinants of the outcome. Then, around a narrow enough window around the threshold $v^*$, we can estimate the causal effect of renewing a road tax levy on the outcome variable $y_{it}$ by comparing the outcome variable for cities that narrowly passed the referendum to those that narrowly failed the referendum \cite{lee_lemieux2010}.

\subsection{Intent to Treat (ITT) Estimator}

We follow a model of Regression Discontinuity Design (RDD) similar to \cite{cellini2010value} and estimate the 'intent to treat' or ITT estimator. We prefer using ITT estimator instead of the alternative "Treatment on the Treated" (TOT) estimator because the ITT estimator is more suited to our setting given the independence of the renewal elections, which we show in Section . As described in \cite{cellini2010value}, when the elections are independent, the ITT estimator equals the TOT estimator.


We operationalize our ITT estimator using the following regression equation -

$$
Y_{i,t+\tau} = \alpha_\tau + \kappa_t + F_{it} \theta_{\tau}^{ITT} + P_g (v_{it}, \gamma_\tau) + Z_{it} \beta_\tau + \epsilon_{i,t + \tau}
$$

Above, we have a municipality $i$ that held an election in year $t$ and we study this municipality's outcome $\tau$ years later. $Y_{i,t+\tau}$ represent the outcome variable for city, village or township $i$ at year $t + \tau$. The outcome variables we study include house prices, wages, and employment. We define treatment as failure of a city, village or township to renew its road maintenance tax levy, which is represented by the indicator $F_{it}$ and $\theta_{\tau}^{ITT}$ is the causal effect of failing to renew road tax on the outcome. $P_g (v_{it}, \gamma_\tau)$ is a polynomial function of the running variable $v_{it}$, which is the percent of votes against the renewal tax levy. $\alpha_\tau$ and $\kappa_t$ represent timing and year-specific fixed effects. We estimate $\theta_{\tau}^{ITT}$ by comparing the outcome variable for cities that narrowly passed the referendum to those that narrowly failed the referendum.        


We use the bandwidth selection method described in \cite{calonico2019regression} to find the mean optimal bandwidth $h$ and then conduct a local polynomial regression after choosing a weighting scheme $k$. The bandwidth $h$ determines size of the neighborhood around the cutoff $v^*$, where the neighborhood is $(v^* - h, v^* + h)$. Only observations with values of the running variable within this neighborhood are used to compute the treatment effect estimate $\hat{\tau}$ and, for a small enough neighborhood, the continuity assumption central to the RDD estimator is satisfied. The weighting scheme $k$ determines the weights of the observations within the neighborhood $(v^* - h, v^* + h)$ and is another important factor in determining $\theta_{\tau}$. The most common types of weighting schemes are uniform, triangular and Epanechnikov. We use the default Mean Squared Error Regression Discontinuity (MSERD) method to compute the effective bandwidth ($h$) and bias bandwidth ($b$) for each outcome variable. This method identifies the bandwidth that minimizes the trade-off between bias and variance of the treatment effect estimate. All observations are used to estimate $h$ and $b$, but only the observations within the selected bandwidth $h$ i.e. effective observations within $h$ percentage points on either side of the vote share cutoff $v^*$ are used to identify our treatment effect estimates $\theta_\tau$, for different $\tau$ years.

