{\bf Related Literature.} Perhaps the study most related to ours is \cite{asher2020}, which studies the impact of new roads on villages in India. Like our study, its identification strategy is regression discontinuity, although ours is sharp rather than the fuzzy form.  It argues the main obstacle to identification in prior studies is that the placement of new roads is usually correlated with economic (or political) characteristics rather than exogenous. Its findings suggest this is a serious problem with the literature because, unlike prior studies, it finds no strong link between economic growth and new road placement, suggesting that the estimates of previous studies that find a link are driven by road placement in villages that are already growing. \cite{asher2020} touts its use of village-level rather than regional-level data.  We, too, look at economic outcomes at the level of village, city, and township, the most local levels of government.  A surprising finding of \cite{asher2020} is that investment in transportation infrastructure does not affect village incomes, assets, or agricultural output.  Its measure of assets is a village-level average of a series of binary indicators of ownership of a variety of assets, along with separate regressions for the presence of a ‘solid house’, refrigerator, and phone; whereas we study the effect of local road tax cuts on housing sale prices.  Of course, our use of a developed geography contrasts with rural villages in India.  Our efforts to achieve identification focus on the maintenance of existing roads, which avoids the endogeneity of the placement of new roads.

Another study related to ours is \cite{cellini2010value}, which studies the effect of new capital projects for schools, funded via new local bond issues and raised by referendums. Both our study and \cite{cellini2010value} employ a dynamic regression discontinuity design and analyze changes in regional property values. Moreover, both papers rely on broadly similar identification strategies and assignment mechanisms: in each case, votes in favor of or against a local referendum serves as the source of exogenous variation. Despite these similarities, a few key distinctions stand out. First, \cite{cellini2010value} draws on all observations in their sample, while we limit our analysis to the optimal bandwidth around the 50\% vote-share cutoff, even after using flexible controls. Second, \cite{cellini2010value} implements a fuzzy regression discontinuity approach, whereas ours is sharp. Lastly, we focus on the Intent-to-Treat (ITT) estimator, which analyzes the effect of an election on outcomes without controlling for the results of subsequent elections. The ITT estimator suits our setting given the independence of renewal referendums characterized by exogenous timing (more details in Section \ref{sec:empirical}). As \cite{cellini2010value} show, when elections are independent, the ITT estimator is equal to the Treatment on the Treated (TOT) estimator. 

% We highlight a substantial literature studying the effect of transportation infrastructure on house prices. \cite{hoogendoorn2019house} studies the effect of the opening of a tunnel on house prices in the Netherlands, noting that prior research studying transportation infrastructure in developed geographies suffers from reverse causality.  It argues that the opening of the Westerscheldtunnel is a fairly exogenous event, with natural borders that prevent contamination of results by the surrounding environment. \cite{hoogendoorn2019house} finds half the capitalized value of the tunnel occurs more than a year before the tunnel opens and argues that the exogeneity of the opening of the tunnel, along with hedonic controls, time trends and postcode fixed effects, identifies its estimates. Our data, too, is for a developed nation. One novelty of our study is how ordinary the events are that we study. While the opening of a new tunnel is important, it is rare.  Votes to renew infrastructure spending are common events in many local governments in the United States, and the quantity of road maintenance spending is regularly chosen by governments around the world, if not by voting then directly by bureaucrats. It is therefore also important to study the effects of road maintenance spending on house prices. 

We highlight a substantial literature studying the effect of transportation infrastructure on house prices. \cite{hoogendoorn2019house} studies the effect of the opening of a tunnel on house prices in the Netherlands, noting that prior research on transportation infrastructure in developed regions often suffers from reverse causality. It argues that the opening of the Westerscheldtunnel is a fairly exogenous event, with natural borders that prevent contamination of results by the surrounding environment. \cite{hoogendoorn2019house} finds that half the capitalized value of the tunnel occurs more than a year before the tunnel opens and argues that the exogeneity of the tunnel's opening, along with hedonic controls, time trends, and postcode fixed effects, identifies its estimates. Our data also pertains to a developed nation. One novelty of our study is how ordinary the events are that we study. While the opening of a new tunnel is significant, it is rare. Votes to renew infrastructure spending are common events in many local governments in the United States, and the amount of road maintenance spending is regularly determined by governments worldwide, either through voting or directly by bureaucrats. It is therefore important to study the effects of road maintenance spending on house prices.

\cite{li2016wheels} studies the overall effect on apartment prices of new subway lines in Beijing, but the estimates may represent the net effect of competing factors. \cite{gibbons2005valuing}, studying the construction of new rail stations for the London underground and light rail services, notes that the effect on house prices captures the net effect of better access, increased crime, and increased noise pollution. \cite{levkovich2016effects} looks at the effect of highway development on house prices in the Netherlands. It separates out accessibility effects from noise pollution and increased traffic effects by looking at different neighborhoods near the highway development. Its repeat sales difference in differences model finds increased house prices from anticipation effects \citep{kohlhase1991impact}. \cite{beenstock2016hedonic} also finds anticipation effects for house prices (but not new construction) for the development of a highway across Israel. 

{\bf Contribution.} Our paper contributes to the literature on three main fronts. First, we establish a new dataset that allows us to study how changes in local taxes affect local infrastructure maintenance and neighborhood house prices.  The votes on road maintenance taxes are matched with auditor data on road maintenance spending by Ohio cities, and property sale prices from CoreLogic. Our data also includes images of roads from Google Street Views API before and after cities vote to cut road maintenance. We train an artificial intelligence model to measure road attractiveness to see if cutting road taxes causes a decline in the physical appearance of roads.  

Second, we focus on long-term effects of reduced road taxes funded mainly via property taxes, and observe statistically significant decline in house prices occurring after four years and persisting in later years. This delayed effect highlights how the consequences of road tax cuts are not immediate but gradually accumulate as funding is reduced and roads deteriorate. Our research also identifies heterogeneous impacts, showing that urban areas and higher-priced houses suffer more pronounced price declines. By focusing on distributional effects, the study adds nuance to the understanding of how infrastructure maintenance affects local housing markets.

Third, while much of the literature focuses on new infrastructure development and expansion in developing nations, we study infrastructure maintenance in a developed economy.  Focusing on existing roads mitigates an important source of identification problems. Our approach provides insights that are more relevant for policymakers in advanced economies, where road infrastructure is well established but requires continuous upkeep. 

{\bf Roadmap.} The rest of the paper is organized as follows. Section \ref{sec:data} provides background information on the data and provides information about the variables used in the study. Section \ref{sec:empirical} outlines the empirical strategy. Section \ref{sec:result} presents the results of the study and shares the relevant robustness checks. Section \ref{sec:mech} suggests some mechanisms and Section \ref{sec:conclusion} concludes. 